Approximating the Optimal State Abstraction

### 2016-04-30 icml_workshop/abstract.tex
abstract.tex

Abstraction is among the most fundamental tools to intelligent agents operating in complex spaces; through abstraction intelligent agents may pare down otherwise prohibitively large problems into tractably solvable fun. Unsurprisingly, then, a great deal of work in planning and \ac{RL} has focused on abstraction in \ac{MDP} in the form of state aggregation and temporally extended actions. However, there exists little work detailing what good abstractions ought to formally accomplish. In this work we propose three desiderata that abstractions in planning and \ac{RL}. We summarize existing work on unifying state aggregation methods, propose an extension of this work to temporally extended actions and suggest how to formally ground out these three desiderata in our extended framework. \enote{Maybe also add experimental results, Dave?}

>>>>

Abstraction is among the most fundamental tools to intelligent agents operating in complex spaces; through abstraction intelligent agents may pare down otherwise prohibitively large problems into tractably solvable ones. Unsurprisingly, a great deal of work in planning and \ac{RL} has focused on abstraction in \ac{MDP} in the form of state aggregation and temporally extended actions. However, there exists little work detailing what good abstractions ought to formally accomplish. In this work we propose three desiderata on abstractions in the context of planning and \ac{RL}. We summarize existing work on unifying state aggregation methods, propose an extension of this work to temporally extended actions and suggest how to formally ground out these three desiderata in our extended framework. \enote{Maybe also add experimental results, Dave?}
